GSS Education Analysis (Working Title)

### 2023-03-15 outputs/paper/paper.qmd
remove unnecessary graphs

## Source and Methodology

@@

The 2021 GSS samples adults over the age of 18 in the United States who do not live in institutional housing **\[citegsscodebook\].** This GSS was released in three batches, the first consisted of 10,091 addresses, the second consisted of 10,000 addresses and the third consisted of 7,500 addresses **\[citegsscodebook\]**. From these three releases, 1,271 completed the survey from the first batch, 1,391 completed the survey from the second batch, and 1,069 completed the survey from the third batch **\[citegsscodebook\].** Meaning that there was an overall response yield of 13.5% or 3,731 complete responses from the 27,591 surveys released **\[citegsscodebook\].**

## Weighting

@@

@@

# Measurement

@@

The United States is built upon individualism, which trickles into their definitions of financial security, happiness, and overall fulfillment and satisfaction in life. Wellbeing of individuals within the United States therefore, is tracked and monitored through a variety of different factors. The aim of this investigation was to determine whether higher educational achievement influenced an individuals perceptions of social class, degree of financial satisfaction and job satisfaction. These factors were chosen because of their significance with regards to the American Dream, a concept that is built off a linear pattern of behavior in terms of economic security. Hustle culture is popular within the United States as an extension of the American Dream, because the idea that an individual must work hard in order to reap the benefits in terms is what drives culture within America.

According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement(citation). These are the fundamentals in terms of how Americans generally define their wellbeing in society. However, no matter how linear an American's personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer. But the ideals of living in the United States, has a powerful impact on culture, and how individuals view themselves and their position within society, but how they fare in comparison to those around them.

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-2
#| fig-cap: "Respondent's Sex by Highest Level of Education"

#### Creating Graph to Compare Sex Against Level of Education ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = degree)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Degree")+
  scale_fill_brewer(palette = "Pastel1")

```{r}
#| echo: false
#| warning: false
#| label: fig-3
#| fig-cap: "Respondent's Sex by Highest Level of Education"

#### Creating Graph to Compare Sex Against Level of Education ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = richwork)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Rich Work")+
  scale_fill_brewer(palette = "Pastel1")
```

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-8
#| fig-cap: "Respondent's Highest Level of Education by Self-Ascribed Social Class"

#### Creating Graph to Compare Sex Against Self-Ascribed Social Class ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Self-Ascribed Class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-9
#| fig-cap: "rich work vs class"

#### Creating Graph ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = richwork, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "richwork",
       y = "number",
       fill = "class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-10
#| fig-cap: "richwork vs satfin"

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = richwork, fill = satfin)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "richwork",
       y = "number",
       fill = "satfin")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-11
#| fig-cap: "richwork vs finrela"

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = richwork, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "richwork",
       y = "number",
       fill = "finrela")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-12
#| fig-cap: "satfin vs satjob"

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = satfin, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "satfin",
       x = "number",
       fill = "satjob")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-13
#| fig-cap: "satfin vs class"

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = satfin, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "satfin",
       x = "number",
       fill = "class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-14
#| fig-cap: "satfin vs finrela"

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = satfin, fill = finrela)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "satfin",
       x = "number",
       fill = "finrela")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-16
#| fig-cap: "finrela vs class"

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = finrela, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "finrela",
       x = "number",
       fill = "class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-19
#| fig-cap: "degree"

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = degree)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "degree",
       x = "number")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-20
#| fig-cap: "happy vs degree"

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = happy)) +
  geom_bar() +
  theme_classic() +
  labs(y = "degree",
       x = "number")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

>>>>

## Source

@@

The 2021 GSS samples adults over the age of 18 in the United States who do not live in institutional housing **\[citegsscodebook\].** This GSS was released in three batches, the first consisted of 10,091 addresses, the second consisted of 10,000 addresses and the third consisted of 7,500 addresses **\[citegsscodebook\]**. From these three releases, 1,271 completed the survey from the first batch, 1,391 completed the survey from the second batch, and 1,069 completed the survey from the third batch **\[citegsscodebook\].** Meaning that there was an overall response yield of 13.5% or 3,731 complete responses from the 27,591 total surveys released **\[citegsscodebook\].**

## Methodology

As mentioned previously, this paper utilizes data from the 2021 US General Social Survey (GSS).

@@

This paper is assessing our estimand 1,567 responses of the 3,731 complete responses received which represents 42% of the complete respondents and only 5.7% of the total surveys released. Respondent's to the 2021 GSS are males or female US citizens, not living in institutional housing, who are over the age of 18 **\[citegsscodebook\]**. In our analysis we removed 2,164 responses to account for unanswered or not applicable responses. We did this to ensure that the data used in this paper is complete and representative of all variables. The variables we selected for our analysis and their measurement levels can be seen in @tbl-1.

@@

@@

The United States is built upon individualism, which trickles into their definitions of financial security, happiness, and overall fulfillment and satisfaction in life. Well-being of individuals within the United States therefore, is tracked and monitored through a variety of different factors. The aim of this investigation was to determine whether higher educational achievement influenced an individuals perceptions of social class, degree of financial satisfaction and job satisfaction. These factors were chosen because of their significance with regards to the American Dream, a concept that is built off a linear pattern of behavior in terms of economic security. Hustle culture is popular within the United States as an extension of the American Dream, because the idea that an individual must work hard in order to reap the benefits in terms is what drives culture within America.

According to Economic Security and the American Dream, the rewards of the American Dream included owning a home, having access to quality health care, having a job that enables an individual to support their family, and having a secure and stately retirement**(citation).** These are the fundamentals in terms of how Americans generally define their well-being in society. However, no matter how linear an American's personal development or educational journey may be, it is simply impossible to be able to guarantee the rewards that the American Dream has to offer. But the ideals of living in the United States, has a powerful impact on culture, and how individuals view themselves and their position within society, but how they fare in comparison to those around them.

@@

@@

@@

@@
